---
title: "H3K9me2 Summary Coverage Plots"
author: "Pablo Monteagudo"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(knitr)    # For knitting document and include_graphics function
```

\newpage

# H3K9me2 Coverage Profiles

```{r H3K9me2 files, echo=FALSE}
seq_category <- "H3K9me2"
#count_mode <- "frac"

coverage_dir <- file.path("/gcm-lfs1/pablo/data/rna_silencing/results", seq_category, "coverage")
all_files <- list.files(path = coverage_dir , pattern = ".pdf", full.names = TRUE, recursive = TRUE)

## counter for visualized samples
total_samples <- 0
```

\newpage

## Samples - WT_H3K9me2

## A. Fractional Coverage

```{r WT frac H3K9me2, echo=FALSE}

sample_name <- "WT_"
count_mode <- "frac"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)

total_samples <- total_samples + length(files)

include_graphics(files)
```

## B. Integer Coverage

```{r WT int H3K9me2, echo=FALSE}

sample_name <- "WT_"
count_mode <- "int"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)

total_samples <- total_samples + length(files)

include_graphics(files)
```

<!-- ## Samples - 80_H3K9me2 (clr4d)-->

<!-- ## A. Fractional Coverage -->

<!-- ```{r 80 frac H3K9me2, echo=FALSE} -->

<!-- sample_name <- "80_" -->
<!-- count_mode <- "frac" -->

<!-- files <- str_subset(all_files, pattern=count_mode) -->
<!-- files <- str_subset(files, pattern=sample_name) -->

<!-- total_samples <- total_samples + length(files) -->

<!-- include_graphics(files) -->
<!-- ``` -->

<!-- ## B. Integer Coverage -->

<!-- ```{r 80 int H3K9me2, echo=FALSE} -->

<!-- sample_name <- "80_" -->
<!-- count_mode <- "int" -->

<!-- files <- str_subset(all_files, pattern=count_mode) -->
<!-- files <- str_subset(files, pattern=sample_name) -->

<!-- total_samples <- total_samples + length(files) -->

<!-- include_graphics(files) -->
<!-- ``` -->

## Samples - 301_H3K9me2 (swi6d)

## A. Fractional Coverage

```{r 301 frac H3K9me2, echo=FALSE}

sample_name <- "301_"
count_mode <- "frac"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)

total_samples <- total_samples + length(files)

include_graphics(files)
```

## B. Integer Coverage

```{r 301 int H3K9me2, echo=FALSE}

sample_name <- "301_"
count_mode <- "int"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)

total_samples <- total_samples + length(files)

include_graphics(files)
```

## Samples - 302_H3K9me2 (clr3d)

## A. Fractional Coverage

```{r 302 frac H3K9me2, echo=FALSE}

sample_name <- "302_"
count_mode <- "frac"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)

total_samples <- total_samples + length(files)

include_graphics(files)
```

## B. Integer Coverage

```{r 302 int H3K9me2, echo=FALSE}

sample_name <- "302_"
count_mode <- "int"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)

total_samples <- total_samples + length(files)

include_graphics(files)
```

## Samples - 324_H3K9me2 (chp2d)

## A. Fractional Coverage

```{r 324 frac H3K9me2, echo=FALSE}

sample_name <- "324_"
count_mode <- "frac"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)

total_samples <- total_samples + length(files)

include_graphics(files)
```

## B. Integer Coverage

```{r 324 int H3K9me2, echo=FALSE}

sample_name <- "324_"
count_mode <- "int"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)

total_samples <- total_samples + length(files)

include_graphics(files)
```

## Samples - 491_H3K9me2 (mit1d)

## A. Fractional Coverage

```{r 491 frac H3K9me2, echo=FALSE}

sample_name <- "491_"
count_mode <- "frac"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)

total_samples <- total_samples + length(files)

include_graphics(files)
```

## B. Integer Coverage

```{r 491 int H3K9me2, echo=FALSE}

sample_name <- "491_"
count_mode <- "int"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)

total_samples <- total_samples + length(files)

include_graphics(files)
```

## Samples - 504_H3K9me2 (rrp6d)

## A. Fractional Coverage

```{r 504 frac H3K9me2, echo=FALSE}

sample_name <- "504_"
count_mode <- "frac"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)

total_samples <- total_samples + length(files)

include_graphics(files)
```

## B. Integer Coverage

```{r 504 int H3K9me2, echo=FALSE}

sample_name <- "504_"
count_mode <- "int"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)

total_samples <- total_samples + length(files)

include_graphics(files)
```

## Samples - 510_H3K9me2 (caf1d)

## A. Fractional Coverage

```{r 510 frac H3K9me2, echo=FALSE}

sample_name <- "510_"
count_mode <- "frac"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)

total_samples <- total_samples + length(files)

include_graphics(files)
```

## B. Integer Coverage

```{r 510 int H3K9me2, echo=FALSE}

sample_name <- "510_"
count_mode <- "int"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)

total_samples <- total_samples + length(files)

include_graphics(files)
```

## Samples - 530_H3K9me2 (exo2d)

## A. Fractional Coverage

```{r 530 frac H3K9me2, echo=FALSE}

sample_name <- "530_"
count_mode <- "frac"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)

total_samples <- total_samples + length(files)

include_graphics(files)
```

## B. Integer Coverage

```{r 530 int H3K9me2, echo=FALSE}

sample_name <- "530_"
count_mode <- "int"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)

total_samples <- total_samples + length(files)

include_graphics(files)
```

## Samples - 638_H3K9me2 (ago1d)

## A. Fractional Coverage

```{r 638 frac H3K9me2, echo=FALSE}

sample_name <- "638_"
count_mode <- "frac"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)

total_samples <- total_samples + length(files)

include_graphics(files)
```

## B. Integer Coverage

```{r 638 int H3K9me2, echo=FALSE}

sample_name <- "638_"
count_mode <- "int"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)

total_samples <- total_samples + length(files)

include_graphics(files)
```


## Total Samples: `r total_samples`