---
title: "S2-ChIP-INPUT/OIN Summary Coverage Plots"
author: "Pablo Monteagudo"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(knitr)    # For knitting document and include_graphics function
```

\newpage

# S2-ChIP-INPUT Coverage Profiles

```{r cars, echo=FALSE}
seq_category <- "INPUT"
count_mode <- "frac"

coverage_dir <- file.path("/gcm-lfs1/pablo/data/rna_silencing/results", seq_category, "coverage")
all_files <- list.files(path = coverage_dir , pattern = ".pdf", full.names = TRUE, recursive = TRUE)

## counter for visualized samples
total_samples <- 0
```


### Samples - WT_S2-ChIP-INPUT

```{r WT_S2-ChIP-INPUT, echo=FALSE}

sample_name <- "WT_"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)
total_samples <- total_samples + length(files)

include_graphics(files)
```

### Samples - 80_S2-ChIP-INPUT

```{r 80_S2-ChIP-INPUT, echo=FALSE}

sample_name <- "80_"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)
total_samples <- total_samples + length(files)

include_graphics(files)
```


### Samples - 301_S2-ChIP-INPUT

```{r 301_S2-ChIP-INPUT, echo=FALSE}

sample_name <- "301_"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)
total_samples <- total_samples + length(files)

include_graphics(files)
```

### Samples - 302_S2-ChIP-INPUT

```{r 302_S2-ChIP-INPUT, echo=FALSE}

sample_name <- "302_"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)
total_samples <- total_samples + length(files)

include_graphics(files)
```

### Samples - 324_S2-ChIP-INPUT

```{r 324_S2-ChIP-INPUT, echo=FALSE}

sample_name <- "324_"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)
total_samples <- total_samples + length(files)

include_graphics(files)
```

### Samples - 491_S2-ChIP-INPUT

```{r 491_S2-ChIP-INPUT, echo=FALSE}

sample_name <- "491_"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)
total_samples <- total_samples + length(files)

include_graphics(files)
```

\newpage

### Samples - 504_S2-ChIP-INPUT

```{r 504_S2-ChIP-INPUT, echo=FALSE}

sample_name <- "504_"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)
total_samples <- total_samples + length(files)

include_graphics(files)
```

\newpage

### Samples - 510_S2-ChIP-INPUT

```{r 510_S2-ChIP-INPUT, echo=FALSE}

sample_name <- "510_"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)
total_samples <- total_samples + length(files)

include_graphics(files)
```

### Samples - 523_S2-ChIP-INPUT

```{r 523_S2-ChIP-INPUT, echo=FALSE}

sample_name <- "523_"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)
total_samples <- total_samples + length(files)

include_graphics(files)
```

### Samples - 524_S2-ChIP-INPUT

```{r 524_S2-ChIP-INPUT, echo=FALSE}

sample_name <- "524_"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)
total_samples <- total_samples + length(files)

include_graphics(files)
```

### Samples - 530_S2-ChIP-INPUT

```{r 530_S2-ChIP-INPUT, echo=FALSE}

sample_name <- "530_"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)
total_samples <- total_samples + length(files)

include_graphics(files)
```

### Samples - 544-ChIP-INPUT

```{r 544_S2-ChIP-INPUT, echo=FALSE}

sample_name <- "544_"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)
total_samples <- total_samples + length(files)

include_graphics(files)
```


### Samples - 638_S2-ChIP-INPUT

```{r 638_S2-ChIP-INPUT, echo=FALSE}

sample_name <- "638_"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)
total_samples <- total_samples + length(files)

include_graphics(files)
```

### Samples - 1022_S2-ChIP-INPUT

```{r 1022_S2-ChIP-INPUT, echo=FALSE}

sample_name <- "1022_"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)
total_samples <- total_samples + length(files)

include_graphics(files)
```


### Samples - 1168_S2-ChIP-INPUT

```{r 1168_S2-ChIP-INPUT, echo=FALSE}

sample_name <- "1168_"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=sample_name)
total_samples <- total_samples + length(files)

include_graphics(files)
```


## Total Samples: `r total_samples`