---
title: "Simulated/Fake reads Summary Coverage Plots"
author: "Pablo Monteagudo"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(knitr)    # For knitting document and include_graphics function
```

\newpage

# Simulated/Fake reads Coverage Profiles

```{r cars, echo=FALSE}
seq_category <- "simulated-data"
#count_mode <- "frac"

coverage_dir <- file.path("/gcm-lfs1/pablo/data/rna_silencing/results", seq_category, "coverage")
all_files <- list.files(path = coverage_dir , pattern = ".pdf", full.names = TRUE, recursive = TRUE)

## counter for visualized samples
total_samples <- 0
```

\newpage

## Fake-reads Samples - Using ChIP Pipeline (Unstranded)

### A. Fractional Coverage

```{r frac fake-reads ChIP, echo=FALSE}

pipeline_mode <- "chip_"
count_mode <- "frac"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=pipeline_mode)

total_samples <- total_samples + length(files)

include_graphics(files)
```

### B. Integer Coverage

```{r int fake-reads ChIP, echo=FALSE}

pipeline_mode <- "chip_"
count_mode <- "int"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=pipeline_mode)

total_samples <- total_samples + length(files)

include_graphics(files)
```

\newpage


## Fake-reads Samples - Using RNA Pipeline (Stranded - Filtered/Tagged)

### A. Fractional Coverage

```{r frac tagged fake-reads RNA, echo=FALSE}

pipeline_mode <- "rna_tagged_fake"
count_mode <- "frac"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=pipeline_mode)

total_samples <- total_samples + length(files)

include_graphics(files)
```

## B. Integer Coverage

```{r int tagged fake-reads RNA, echo=FALSE}

pipeline_mode <- "rna_tagged_fake"
count_mode <- "int"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=pipeline_mode)

total_samples <- total_samples + length(files)

include_graphics(files)
```

\newpage


### Fake-reads Samples - Using RNA Pipeline (Stranded)

## A. Fractional Coverage

```{r frac fake-reads RNA, echo=FALSE}

pipeline_mode <- "rna_fake"
count_mode <- "frac"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=pipeline_mode)

total_samples <- total_samples + length(files)

include_graphics(files)
```

## B. Integer Coverage

```{r int fake-reads RNA, echo=FALSE}

pipeline_mode <- "rna_fake"
count_mode <- "int"

files <- str_subset(all_files, pattern=count_mode)
files <- str_subset(files, pattern=pipeline_mode)

total_samples <- total_samples + length(files)

include_graphics(files)
```

\newpage

## Total Samples: `r total_samples`