---
title: "Manuscript Plots - Silencing Project"
author: "Pablo Monteagudo"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
header-includes:
  - \usepackage{subfig}
  - \usepackage{float}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(knitr)    # For knitting document and include_graphics function
#library(cowplot)
#library(patchwork)

```

\newpage

```{r get_files, echo=FALSE}
#seq_category <- "Ratios"

# img_dir <- file.path("/gcm-lfs1/pablo/data/rna_silencing/results/Ratios/Plots")
# img_dir <- file.path("/gcm-lfs1/pablo/data/rna_silencing/results/Ratios/Plots_v2")
# img_dir <- file.path("/gcm-lfs1/pablo/data/rna_silencing/results/Ratios/Plots_591")
#img_dir <- file.path("/gcm-lfs1/pablo/data/rna_silencing/results/Ratios/Plots_24-08-20")
#img_dir <- file.path("/gcm-lfs1/pablo/data/rna_silencing/results/Ratios/Plots_04-11-20")
#img_dir <- file.path("/gcm-lfs1/pablo/data/rna_silencing/results/Ratios/Plots_21-01-21")
#img_dir <- file.path("/gcm-lfs1/pablo/data/rna_silencing/results/Ratios/Plots_29-03-21")
img_dir <- file.path("/gcm-lfs1/pablo/data/rna_silencing/results/Ratios/Plots_23-05-21")


#all_files <- list.files(path = img_dir , pattern = ".png", full.names = TRUE, recursive = TRUE)
all_files <- list.files(path = img_dir , pattern = ".pdf", full.names = TRUE, recursive = TRUE)

```

### Figure 1 - 

```{r Figure 1a, echo=FALSE, fig.show = "hold", out.width = "30%", fig.align = "default"}

sample_name <- "Figure1"

files <- str_subset(all_files, pattern=sample_name)

include_graphics(files)
```

```{r Figure 1b, echo=FALSE, fig.show = "hold", out.width = "40%", fig.align = "default"}
#include_graphics(files[3:3])
```

\newpage

### Figure 2 - 

```{r Figure 2a, echo=FALSE, fig.show = "hold", out.width = "30%", fig.align = "default"}

sample_name <- "Figure2"

files <- str_subset(all_files, pattern=sample_name)

include_graphics(files)
```

```{r Figure 2b, echo=FALSE, fig.show = "hold", out.width = "40%", fig.align = "default"}

#include_graphics(files[3:3])
```

\newpage


### Figure 3 - 


<!-- ```{r Figure 3, echo=FALSE} -->


<!-- sample_name <- "Figure3" -->

<!-- files <- str_subset(all_files, pattern=sample_name) -->

<!-- p1 <- ggdraw() + draw_image(files[1], scale = 1) -->
<!-- p2 <- ggdraw() + draw_image(files[2], scale = 1) -->
<!-- p3 <- ggdraw() + draw_image(files[3], scale = 1) -->
<!-- p4 <- ggdraw() + draw_image(files[4], scale = 1) -->
<!-- p5 <- ggdraw() + draw_image(files[5], scale = 1) -->
<!-- p6 <- ggdraw() + draw_image(files[6], scale = 1) -->

<!-- plot_grid(p1, p2, -->
<!--           p3, p4, -->
<!--           p5, p6, -->
<!--           align="hv", -->
<!--           rel_widths = c(3, 1), -->
<!--           ncol= 2) -->

<!-- ``` -->

```{r Figure 3, echo=FALSE, out.extra = "", fig.pos = "H", fig.align = "default", out.width = "0.48\\textwidth",  fig.ncol = 2}

sample_name <- "Figure3"

files <- str_subset(all_files, pattern=sample_name)
files <- str_subset(files, pattern="extra-ccr4-not", negate = TRUE)

include_graphics(files)


```

\newpage

### Figure 3 - Additional Ccr4-Not complex mutants

```{r Figure 3 extra, echo=FALSE, out.extra = "", fig.pos = "H", fig.align = "default", out.width = "0.48\\textwidth",  fig.ncol = 1}

sample_name <- "Figure3"

files <- str_subset(all_files, pattern=sample_name)
files <- str_subset(files, pattern="extra-ccr4-not", negate = FALSE)

include_graphics(files)


```

\newpage

### Figure 5 - 

```{r Figure 5, echo=FALSE, fig.show = "hold", out.width = "80%", fig.align = "center"}

#sample_name <- "Figure5"
sample_name <- "Figure5-A_stranded.pdf"

files <- str_subset(all_files, pattern=sample_name)

include_graphics(files)
```

\newpage

# Manuscript Supplementary Plots - Silencing Project

\newpage

### Supplementary Figure 1 - 

```{r Figure S1a, echo=FALSE, fig.show = "hold", out.width = "50%", fig.align = "default"}

sample_name <- "Figure-S1"

files <- str_subset(all_files, pattern=sample_name)

include_graphics(files)
```

\newpage

### Supplementary Figure 2 - 

```{r Figure S2a, echo=FALSE, fig.show = "hold", out.width = "50%", fig.align = "default"}

sample_name <- "Figure-S2"

files <- str_subset(all_files, pattern=sample_name)

include_graphics(files)
```


### Supplementary Figure 3 - 

```{r Figure S3a, echo=FALSE, fig.show = "hold", out.width = "50%", fig.align = "default"}

sample_name <- "Figure-S3"

files <- str_subset(all_files, pattern=sample_name)
files <- str_subset(files, pattern="extra-ccr4-not", negate = TRUE)

include_graphics(files)
```

\newpage

### Supplementary Figure 3 - Additional Ccr4-Not complex mutants

```{r Figure S3a extra, echo=FALSE, fig.show = "hold", out.width = "50%", fig.align = "default"}

sample_name <- "Figure-S3"

files <- str_subset(all_files, pattern=sample_name)
files <- str_subset(files, pattern="extra-ccr4-not", negate = FALSE)

include_graphics(files)


```

\newpage

# Manuscript Additional Plots - Silencing Project

\newpage

### Intron/Gene Counts Ratio Figure 


```{r Figure Splice ratio, echo=FALSE, fig.show = "hold", out.width = "50%", fig.align = "default"}

files <- "/home/pmonteagudo/workspace/silencing_project/results/splice_ratio.pdf"
include_graphics(files)
```


### tRNAs/mRNAs Ratio Figure 


```{r Figure tRNAs ratio, echo=FALSE, fig.show = "hold", out.width = "50%", fig.align = "default"}

files <- "/home/pmonteagudo/workspace/silencing_project/results/trna_ratios.pdf"
include_graphics(files)
```


<!-- ### INPUT Factors Figure - Average INPUT factor per Mutant type computed using (...) -->


<!-- ```{r INPUT factors, echo=FALSE, fig.show = "hold", out.width = "50%", fig.align = "default"} -->

<!-- files <- "/home/pmonteagudo/workspace/silencing_project/results/input_factors.pdf" -->
<!-- include_graphics(files) -->
<!-- ``` -->

